Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection

### 2014-07-31 paper-for_arxiv/intro.tex
modified sentence in intro

%A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}. See~\cite{fortunato2010community} for a recent review. 
A large body of work exists on methods for automatic detection of communities within networks, among which we recall the Girvan and Newman algorithm~\cite{newman2004finding}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed. As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach. We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then perform the network collection and community detection with that community type in mind.

>>>>

%A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}. See~\cite{fortunato2010community} for a recent review. 
A large body of work exists on methods for automatic detection of communities within networks, among which we recall the Girvan and Newman algorithm~\cite{newman2004finding}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed. As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach. We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration (for example, are we looking for groups of friends, or for groups of people having a common interest?), and then perform community detection with that community type in mind.
